\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{SmarteRun: Coding The Portable Coach}

### 2014-05-13 final/article.tex

>>>>

The results obtained in this investigation show that our approach provides reasonable performance at predicting run paces based on incomplete data. Our overall RMSE in predicting pace over 5000 samples was $2.3088$, which is relatively small over a group of paces that range from $1$ to $7$ meters per second. However, we must also view this in light of our training data. Most of the runs we had in our data set were less than 4 kilometers long, as these were the most common runs that we were able to collect data for. Because of this, our algorithm performs very strongly on shorter runs (RMSE of $0.8771$). This leads us to believe that with additional training data for longer runs, there is potential to decrease the error of our approach significantly.
